---
title: "Predicting in Retail Clothing"
author: "Chloe White"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(Stat2Data)
data("Clothing")
attach(Clothing)
```

### Exercise 1

Insert any text here.

```{r 1}
Clothing2 <- subset(Clothing, Amount != 0 & Amount != 1506000)
mean(Clothing2$Amount)
mean(Clothing2$Dollar12)
```

### Exercise 2

Amount is positively associated with every variable except for Recency. 

```{r 2}
pairs(Clothing2[,2:7])
cor(Clothing2[,2:7])
library(corrplot)
cor(Clothing2[,2:7]) |> corrplot(method="circle")
```

### Exercise 3

Insert any text here.

```{r 3}
model1 <- lm(Amount ~ Dollar12, data = Clothing2)
summary(model1)
plot(Amount ~ Dollar12, data = Clothing2)
abline(model1, col="Blue", lwd=2)
model2 <- lm(Amount ~ Dollar12 + Dollar24 + Recency, data = Clothing2)
summary(model2)
```

### Exercise 4

Insert any text here.

```{r 4}
model3 <- lm(Amount ~ Dollar12 + Freq12 + Dollar24 + Freq24 + Recency + Card, data = Clothing2)
summary(model3)
anova(model1, model3)
```
### Exercise 5

Insert any text here.

```{r 5}
model4 <- lm(Amount ~ Dollar12 + Freq12, data = Clothing2)
summary(model4)
```

### Exercise 6

The P-value is 2.78x10^-13. This indicates that model4 provides better predictions than model1.

```{r 6}
anova(model1, model4)
```

### Exercise 7

I would pick model 4 because it had a smaller p-value. In exercise 6 we saw that model 4 was better than model 1 when looking at the p-value. In this exercise model 3 had a higher p-value when comparing it to model4. That is why I would pick model4. 

```{r 7}
anova(model4, model3)
```

### Exercise 8

Insert any text here.

```{r 8}
Clothing2$AvgSpent12 <- Clothing2$Dollar12/Clothing2$Freq12
model5 <- lm(Amount ~ AvgSpent12, data = Clothing2)
summary(model5)
```

### Exercise 9

Insert any text here.

```{r 9}
library(ggplot2)
qplot(fitted(model5), resid(model5), geom=c("point", "smooth"))
```

### Exercise 10

Insert any text here.

```{r 10}
Clothing2$AvgSpent12Sq <- Clothing2$AvgSpent12^2
model6 <-lm(Amount ~ AvgSpent12 + AvgSpent12Sq, data = Clothing2)
summary(model6)
library(ggplot2)
qplot(fitted(model6), resid(model6), geom=c("point", "smooth"))
plot(fitted(model6), resid(model6))
abline(h=0, col = "blue")
```

### Exercise 11

Insert any text here.

```{r 11}
plot(Amount ~ AvgSpent12, data = Clothing2)
curve(coef(model6)[1] + coef(model6)[2]*x + coef(model6)[3]*x^2, col="blue", lwd=2, add=T)
```

...

